Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements

### 2025-04-14 Submission.tex
omitting one extra analysis

>>>>

Another interesting avenue for future research is to explore these patterns by job type. Kubicek et al. (2023), for instance, found that employee workload was positively related to strain, and that this relationship was stronger for care and social workers compared to other types of employees. This finding suggests that job type may be an important moderator, and worthy of exploration moving forward.
